---
title: "Aci_fitting"
author: "Julien LAMOUR"
date: "10/16/2020"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(LeafGasExchange)
```

# Simulating an Aci curve
For this exemple we first simulate a photosynthesis curve, but it would work the same if the data were not simulated but measured. The data simulation is done using the function f.A. This function needs a list of photosynthetic parameters which are produced using the function f.make.param() and a list of input variables (CO2 at the surface of the leaf, leaf temperature, incdent light, RH)

```{r}
param=f.make.param(VcmaxRef = 50,JmaxRef=50*1.7,TpRef=50/10)
CO2=seq(50,1500,50)
Tleaf=30+273.16
Tair=27+273.16
PAR=1800
RH=80
simul=f.A(PFD = PAR,cs = CO2,Tleaf = Tleaf,Tair = Tair,RH = RH,param = param)
simul$A=simul$A+rnorm(n = length(CO2),mean = 0,sd = 0.4)
measures=data.frame(Tleaf=Tleaf,Ci=simul$ci,PARi=PAR,Photo=simul$A)
```

We display this simulated curve using the function f.plot

```{r}
f.plot(measures = measures,type = 'Aci',list_legend = param[c('VcmaxRef','JmaxRef','TpRef','RdRef')],param = param)
```



#Fitting an Aci curve

To fit an Aci curve, it is necessary to detail the parameter that we want to estimate. All the parameters present in f.make.param can potentially be fitted even if it would not always make sense. We do a first fitting with only the parameters VcmaxRef, JmaxRef and RdRef. Those parameters have to be given in the list Start, with initial values. The method will look for different initial values around those values so it is not necessary to give very good ones, just not too stupid ones. The photosynthetic parameters have to be given in the list param. This is used to determine what should be the parameters for the temperature dependence, for the leaf absorbance, theta, etc.

```{r}
fitting1=f.fitting(measures = measures,Start = list(JmaxRef = 30, VcmaxRef = 50, RdRef = 1),param=f.make.param(),modify.init=TRUE,do.plot=TRUE,type='Aci')
```
In a second example we now also fit TpRef

```{r}
fitting2=f.fitting(measures = measures,Start = list(JmaxRef = 30, VcmaxRef = 50, RdRef = 1,TpRef=9),param=f.make.param(),modify.init=TRUE,do.plot=TRUE,type='Aci')
```

The fitting corresponds to a list of 2 objects. The first object corresponds to the fitting using a minimum square function whereas the second object corresponds to a maximum likelihood which is made using the package mle2. This latter method is usefull because it allowed us to calculate the confidence interval of the parameters:

```{r warning=FALSE}
confint(fitting2[[2]])
```


