---
title: "Aci_fitting"
author: "Julien LAMOUR"
date: "10/16/2020"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(LeafGasExchange)
library(mvtnorm)
```

# Fitting an Aci curve

The objectif of this tutorial is to show how to fit an Aci curve using the LeafGasExchange package. In this tutorial, an Aci curve is first simulated with known photosynthetic parameters and noise. This curve is then fitted to retrieve the parameters.


## Simulating an Aci curve

For this exemple we first simulate a photosynthesis curve, but it would work the same if the data were not simulated but measured. The data simulation is done using the function f.A. This function needs a list of photosynthetic parameters which are produced using the function f.make.param() and a list of input variables (CO2 at the surface of the leaf, leaf temperature, incident light, RH). Too have more information on the function f.make.param, you can use the command ?f.make.param in R console.


```{r}
param=f.make.param(VcmaxRef = 50,JmaxRef=50*1.7,TpRef=50/10)
CO2=seq(50,1500,50)
Tleaf=30+273.16
Tair=27+273.16
PAR=1800
RH=80
simul=f.A(PFD = PAR,cs = CO2,Tleaf = Tleaf,Tair = Tair,RH = RH,param = param)

# Here we include a normal error with a standard deviation proportionnal to the gross photosynthesis (as it is often observed)

noise=unlist(lapply(X = simul$Ag,FUN = function(x){rnorm(n=1,mean=0,sd=0.035*(x))}))
simul$A=simul$A+noise
measures=data.frame(Tleaf=Tleaf,Ci=simul$ci,PARi=PAR,Photo=simul$A)
```

We display this simulated curve using the function f.plot

```{r}
f.plot(measures = measures,type = 'Aci',list_legend = param[c('VcmaxRef','JmaxRef','TpRef','RdRef')],param = param)
```



## Fitting an Aci curve

To fit an Aci curve, it is necessary to detail the parameter that we want to estimate. All the parameters present in f.make.param can potentially be fitted even if it would not always make sense. We do a first fitting with only the parameters VcmaxRef, JmaxRef and RdRef. Those parameters have to be given in the list Start, with initial values. The method will look for different initial values around those values so it is not necessary to give very good ones, just not too stupid ones. The photosynthetic parameters have to be given in the list param. This is used to determine what should be the parameters for the temperature dependence, for the leaf absorbance, theta, etc. By default, the equations and parameters used in the TBM FATES to simulate the photosynthesis are used. In this example, we also give a very high value to TpRef so the TPU limitation is not considered when fitting the curve.


```{r warning=FALSE}
fitting1=f.fitting(measures = measures,Start = list(JmaxRef = 30, VcmaxRef = 50, RdRef = 1),param=f.make.param(),modify.init=TRUE,do.plot=TRUE,type='Aci')
```

In a second example we now also fit TpRef

```{r warning=FALSE}
fitting2=f.fitting(measures = measures,Start = list(JmaxRef = 30, VcmaxRef = 50, RdRef = 1,TpRef=9),param=f.make.param(),modify.init=TRUE,do.plot=TRUE,type='Aci')
```

The fitting corresponds to a list of 2 objects. The first object corresponds to the fitting using a minimum square function whereas the second object corresponds to a maximum likelihood which is made using the package mle2. This latter method is usefull because it allowes us to calculate the confidence interval of the parameters. The mean parameters used to simulate the curves (VcmaxRef = 50,JmaxRef=85,TpRef=5, RdRef=1.43 and sigma_b= 0.035) should be in the confidence interval.

```{r warning=FALSE}
confint(fitting2[[2]])
```

It is possible to compare the AIC of the two models using the base function AIC. The lower AIC corresponds to the best model, showing that in this case and as expected, the TPU limitation is usefull to improve the fit of the model.

```{r}
AIC(fitting1[[2]])
AIC(fitting2[[2]])
```

It is also possible to calculate the interval of confidence and prediction of the Aci curve from the outputs of the fitting.

```{r}
var_cov=fitting2[[2]]@vcov
random_param=rmvnorm(1000,mean=fitting2[[2]]@coef[c('sigma_b','JmaxRef','VcmaxRef','TpRef','RdRef')],sigma = var_cov)

random_simul=matrix(data = NA,nrow = 1000,ncol = nrow(measures))
for(i in 1:1000){
  random_simul[i,]=f.Aci(PFD = measures$PARi,ci = measures$Ci,Tleaf =measures$Tleaf,param = f.make.param(VcmaxRef=random_param[i,'VcmaxRef'],JmaxRef=random_param[i,'JmaxRef'],TpRef=random_param[i,'TpRef'],RdRef=random_param[i,'RdRef']))$A
}

fit_pred=f.Aci(PFD = measures$PARi,ci = measures$Ci,Tleaf =measures$Tleaf,param = f.make.param(VcmaxRef=fitting2[[2]]@coef[c('VcmaxRef')],JmaxRef=fitting2[[2]]@coef[c('JmaxRef')],TpRef=fitting2[[2]]@coef[c('TpRef')],RdRef=fitting2[[2]]@coef[c('RdRef')]))

sd_mean=apply(X = random_simul,MARGIN = 2,FUN =sd)
sd_res=fitting2[[2]]@coef['sigma_b']*fit_pred$Ag
sd_tot=sqrt(sd_mean^2+sd_res^2)
simul_confint=rbind(fit_pred$A-1.96*sd_mean,fit_pred$A+1.96*sd_mean)
simul_pred=rbind(fit_pred$A-1.96*sd_tot,fit_pred$A+1.96*sd_tot)

f.plot(measures = measures,type = 'Aci',list_legend = param[c('VcmaxRef','JmaxRef','TpRef','RdRef')],param = param)
polygon(c(measures$Ci ,rev(measures$Ci)),c(simul_pred[1,], rev(simul_pred[2,])),
        col=adjustcolor("lightgrey",alpha.f=0.5),border=NA)
polygon(c(measures$Ci ,rev(measures$Ci)),c(simul_confint[1,], rev(simul_confint[2,])),
        col=adjustcolor("#99CC99",alpha.f=0.5),border=NA)
```

