---
title: "How_to_simulate_Photosynthesis"
author: "Julien LAMOUR"
date: "9/22/2020"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of the photosynthesis model

The package LeafGasEx can be used to simulate the photosynthesis at the leaf level using the function f.AT(). The FvCB photosynthesis model (Farquhar et al. 1980) is coupled with the USO model (Medlyn et al. 2011) and an energy balance model (Muir 2019). 

The input variables for this model are:
-Photosynthetic photon flux density, PFD in micro mol m-2 s-1
-CO2 at the surface of the leaf, cs in ppm
-Air temperature at the surface of the leaf, Tair in degree K
-Air relative humidity, RH in % (between 0 and 100)
-Wind speed at the surface of the leaf, wind in m s-1

The parameters for this function are the parameters of the photosynthesis and stomata models. The list of parameters is described in the help of the function f.make.param. It includes notably the parameters Vcmax, Jmax, Tp, Rd at 25 degree C and g0 and g1.

In addition to those parameters, the parameters precision and max_it can be modified. By default there value are 0.1 and 10 respectively. The energy budget is calculated iteratively. Temperature convergence is achieved when the prior leaf temperature which is guessed and the predicted temperature are within the accuracy range (default 0.1 degree C). If more than max_it iterations are needed for the temperatures to converge, then the calculation stops.

The output variables are:
- the net assimilation A in micro mol m-2 s-1
- the leaf water conductance gs in mol m-2 s-1
- The CO2 concentration inside the stomata cavity, ci in ppm
- The leaf temperature Tleaf in degree K
- The vapour pressure deficit between the leaf and the surounding atmosphere ds in kPa

## Cretion of a list of parameters used by the f.AT() function

The function f.make.param() can be used to create a list of photosynthetic parameters. By default, the parameters are the one from the Functionnaly Assembled Terrestrial Ecosystem Simulator for tropical species.

```{r}
param<-f.make.param()
print(param)
```

It is possible to change some or all of the parameters by modifying the parameters in the call of the function f.make.param()

```{r}
param<-f.make.param(JmaxRef = 100,VcmaxRef = 60,RdRef = 1,g0 = 0.02,g1=4)
print(param)
```

## Predicting the photosynthesis 

Prediction of the photosynthesis using the previous list of parameters and different leaf conditions is done in the following way:

```{r}
Leaf_photo=f.AT(PFD = 1000,cs = 400,Tair = 273.15+29,RH = 70,wind = 2,param = param)
print(Leaf_photo)
```



## References

Farquhar, G.D., von Caemmerer, S. & Berry, J.A. A biochemical model of photosynthetic CO2 assimilation in leaves of C3 species. Planta 149, 78–90 (1980). https://doi.org/10.1007/BF00386231

Medlyn, B.E., Duursma, R.A., Eamus, D., Ellsworth, D.S., Prentice, I.C., Barton, C.V.M., Crous, K.Y., De Angelis, P., Freeman, M. and Wingate, L. (2011), Reconciling the optimal and empirical approaches to modelling stomatal conductance. Global Change Biology, 17: 2134-2144. doi:10.1111/j.1365-2486.2010.02375.x

Christopher D Muir, tealeaves: an R package for modelling leaf temperature using energy budgets, AoB PLANTS, Volume 11, Issue 6, December 2019, plz054, https://doi.org/10.1093/aobpla/plz054
